Model Checking

### 2024-01-11 owen/Write Ups/04_model_checking.qmd
starting to update the report with the full fits

@@

### 1700-1900 Players

We fit this to games from 25 players in the 1700-1900 range. 
We looked only at standard rated bullet games (no tournaments, etc),
which was 445k games, ranging from 500 - 50k games per player.
Fitting this model take over 12 hours on a computing cluster.

@@

```{r}
fit <- readRDS(here("results/", "lichess1700-1900/", 
                    "all_rated_bullet_model3.RDS"))

@@

@@

- Here the mean for $\mu_2$ is -0.0651, corresponding to a 48% chance of 
winning as black against an equally ranked opponent. This parameter
is not clearly different from 0 here. Posterior SD is large.

- $\gamma_1$ is estimated to be about 0.115, indicating that playing 
as white increases the win probability by 3%, holding other parameters 
fixed. Posterior SD is very small.

@@

```{r get names 1700-1900}
#| cache: true

## need to get user names here, from the data again

data_path <- here("box_data/lichess1700-1900/")

users <- unique(small_data$Username)

```{r winner-effects-17-19}
#| fig.height = 7

@@

>>>>

This is being updated now to show all players in the Box Data.

@@

### 1700-1900 Players, Bullet

We fit this to games from all players in the 1700-1900 range. 
We looked only at standard rated bullet games (no tournaments, etc),
which 675k games, ranging from 500 - 128k games per player.
Fitting this model takes many hours on a computing cluster.

@@

```{r}
fit <- readRDS(here("results/", "Full_Fits", "lichess1700-1900/", 
                    "all_rated_bullet_model.RDS"))

users <- readRDS(here("results/", "Full_Fits",
                      "lichess1700-1900/",
                      "users_bullet.RDS"))

@@

fit$summary(variables = c("mu1", "mu2", "gamma1", "gamma2"))

@@

- Here the mean for $\mu_2$ is -0.0483, corresponding to a 48% chance of 
winning as black against an equally ranked opponent. This parameter
is not clearly different from 0 here. Posterior SD is large.

- $\gamma_1$ is estimated to be about 0.094, indicating that playing 
as white increases the win probability by 2.5%, holding other parameters 
fixed. Posterior SD is very small.

@@

```{r winner-effects-17-19}
#| fig.height = 9

@@

<!-- Down to here in terms of updating this -->
